Grounding the Interaction: Anchoring Situated Discourse in Everyday Human-Robot Interaction

### 2011-10-21 paper_knowledge.tex
Make clearer that we use tag to initialize knowledge

\subsection{Informational Content Extraction}

@@

@@

\subsubsection{Modeling the Real World}

@@

>>>>

\subsection{Informational Content Extraction}
\label{informational_content_extraction}

@@

We discuss in section~\ref{modeling_real_world} how the initial knowledge (the
existence of a yellow banana) can be acquired.

@@

\subsubsection{Modeling the Real World}
\label{modeling_real_world}

@@

Note also that, as mentioned in section~\ref{spygame}, perception issues have
been skipped in our experiments by using a tag-based object identification
method. In section~\ref{informational_content_extraction}, we give an example
where the human says ``the yellow banana is big''. It is assumed in the example
that the robot already knows about a banana instance that is yellow. In our
experiments, this kind of knowledge was either hard coded in scenario-specific
ontologies (with facts like \stmt{BANANA1 type Banana} where \concept{BANANA1}
is the id of the banana's tag) or taught to the robot with prescriptive
sentences like ``Learn that this is a banana'' while pointing at the banana's
tag.

It would be interesting to broaden this approach with automatic classifiers
(for colour, size, etc.). If the robot later discovers a yellowish and large
object, an utterance like ``the yellow banana is big'' could be used to assert
that this very object is in fact a banana. A similar approach has been 
developed by~\cite{Vrecko2009}.
